\textbf{Computational Fuzzy Extractors}

### 2013-02-26 trunk/CompFuzzExt.tex
Notes in Unp impossibility section

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.% with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-1,t)$ (information-theoretic) secure sketch with error
$2(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Defining  Computational Fuzzy Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $X$ be an arbitrary distribution of min-entropy $m$.  Let $Y$ be a distribution over $\mathcal{M}$ with $\Hoo(Y)\geq k$ such that 
\[ 
\delta^{\mathcal{D}_s}((X, \sketch(X)), (Y, \sketch(X)))<\epsilon.
\]  
where  $s = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
  By correctness of the sketch $ \expe D(X, \sketch(X)) \ge 1-\delta$.  Since 
$\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon.$ then $D(Y, SS(X))>1-\epsilon-\delta$.  This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
%This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
Thus, for all $t', 1\leq t'\leq t$ on a random $y$
\[ \Pr_{y\leftarrow Y}[y'\leftarrow \sample(y, t') \wedge \rec(y', \sketch(x')) = y]\geq 1-\epsilon-\delta.\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot, \sketch(x'))$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

>>>>

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

\corref{cor:rec yields sketch} extends to non-uniform distributions: if there exists a distribution whose HILL sketch retains $\tilde{m}$ bits of entropy, then for all distributions $W$, there is an information theoretic sketch that retains $\Hoo(W) - (n\log |Z|-\tilde{m})-2$ bits of entropy.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).

Unfortunately, unpredictability entropy must also decrease with $t$.  That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  The formal statement is below~(proof in \secref{sec:proof of imp unp entropy})
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution $Y$ actually contains many points.  This means we cannot construct a good code out of the points of $Y$.  Our bound is a result of the Hamming bound for the space.  
\subsection{Defining  Computational Fuzzy Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ such that 
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
\]  
where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-\delta$.  Since 
$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-\delta$.  By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + \delta)$.  Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.  Then 
\[
\Hav(Y  | W) = -\log \left( \Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} + \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})} \right)
\] 
Rearranging terms:
\begin{align*}
\Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} &= 2^{-\Hav(Y  | W) } - \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})}\\
&=2^{-\Hav(Y  | W) } = 2^{-k}
\end{align*}
This means that $2^{-\Hav(Y | W\in 1_{S_W})} \geq 2^{-k}/\Pr[W\in 1_{S_W}] = 2^{-k+1}$.  That is, $\Hav(Y|W\in 1_{S_W})\geq k-1$.  Fix one value $s \in 1_{S_W}$ such that $\Hav(Y | s)\geq k-1$.
%This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
%This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
Thus, for all $t', 1\leq t'\leq t$ on a random $y$
\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y$ is a $(t, \epsilon)$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}
